---
title: "Creation of the automatical documentation for package"
author: "Florine Garcia and Pierre L'Hermite"
date: "13 mars 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1) Packages

3 packages are needed to create automaticall short documentation for each function  

```{r}
library(devtools) # Contain function document()
library(roxygen2) # Create automatical documentation
```
The last package Rtools must be downloading with this link :
[Package](https://cran.r-project.org/bin/windows/Rtools/)

## 2) Headings

The [template](https://github.com/flogrc/piflow/blob/master/R/Template_function.R)
gives an example of the minimal information for each function.

Different sections begin by @something and sections can be in different order
except for the first two sections (short resume of function and the explanation
of the function)  

**Tips :**  
* Start a line   
```{r}
#'
```
* Italics  
```{r}
#'\emph{}
```
* Bold  
```{r}
#'\string{}
```
* Look like code  
```{r}
#'\code{}
```
* Text wrapping  
```{r}
#'\cr
```
* Bullet point, you can include different itemize and there are different type
of bullet point (\enumerate, \itemize, \describe)  
**Example :**  
```{r}
#'\itemize
#'    @return zoo  
#'    \itemize{  
#'    \item Wet  
#'    \item Normal  
#'    \item Dry  
#'    }
```
**Problem**
```{r}
#'\% replace %  
```

More informations are available on different website :  
[R package](http://r-pkgs.had.co.nz/man.html)  
[Mastering Software Development in R](https://bookdown.org/rdpeng/RProgDA/documentation.html)  
[Text formatting reference sheet](https://cran.r-project.org/web/packages/roxygen2/vignettes/formatting.html)  
[Learning more about Markdown](http://r-pkgs.had.co.nz/vignettes.html)

## 3) Creation of documentation

1. Create your function with the new heading with roxygen2 (see part 2 Heading)  
2. Delete all files in man folder of your package
3. Use a function of devtools package
```{r eval = FALSE}
devtools::document()
```
4. Install and restart package in the "build" tab, your package will be check and
install in your Rstudio session (Ctrl+Shift+B)  
5. Check the result with the "help" tab with your different function  
6. Restart your creation for each function or if you want to improve one